
\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\title{Git Tutorial for Computer Science Students}
\author{}
\date{}

\begin{document}

\maketitle

\section{Introduction}

Git is a distributed version control system. This tutorial is designed to introduce Computer Science major students to the fundamentals of using Git. We will focusing on the basics of Init-ing/Cloning, Adding, Committing, Pushing, and topic of stashes, branches, merging and dealing with conflicts. By the end of the tutorial, you should have a basic understanding of how to use Git to manage your code.

\section{Setting Up Git}

Before starting, ensure you have Git installed on your computer. You can verify this by opening a terminal and typing:

\begin{lstlisting}[language=bash]
git --version
\end{lstlisting}

If Git is not installed, please visit \href{https://github.com/} to download and install it.

\section{Git Basics}


\subsection{Init}

\begin{lstlisting}[language=bash]
git init
\end{lstlisting}

This command creates a new Git repository in your project directory.

\subsection{Clone}

\begin{lstlisting}[language=bash]
git clone https://repository-url.git
\end{lstlisting}

Replace https://repository-url.git with the actual URL of the repository.

\subsection{Add}

\begin{lstlisting}[language=bash]
git add filename
\end{lstlisting}

To track changes to a file or files.

\subsection{Commit}

\begin{lstlisting}[language=bash]
git commit -m "Commit message"
\end{lstlisting}

To save your changes, commit them to the repository with a message.

\subsection{Push}

\begin{lstlisting}[language=bash]
git push origin main
\end{lstlisting}

To upload your local commits to a remote repository.

\section{Using Branches}

To manage new features or experiments in your project, you can use branches. This allows you to work on different versions of your project simultaneously without affecting the main codebase.

\subsection{Create a New Branch}

\begin{lstlisting}[language=bash]
git branch feature-x
\end{lstlisting}

\subsection{Switch to the New Branch}

\begin{lstlisting}[language=bash]
git checkout feature-x
\end{lstlisting}

Alternatively, create and switch to a new branch in one command:

\begin{lstlisting}[language=bash]
git checkout -b feature-x
\end{lstlisting}

\section{Making Changes and Stashing}

While working on your project, you might want to save your work without committing it. Git stash is useful in this scenario.

\subsection{Make Some Changes}

Let's modify `hello.py`:

\begin{lstlisting}[language=Python]
print("Hello, Git from feature-x!")
\end{lstlisting}

\subsection{Stash Your Changes}

If you're not ready to commit:

\begin{lstlisting}[language=bash]
git stash
\end{lstlisting}

\subsection{Apply Your Stashed Changes}

When ready to continue:

\begin{lstlisting}[language=bash]
git stash pop
\end{lstlisting}

\section{Merging Changes}

After completing your work on a branch, you may want to merge those changes back into the main branch.

\subsection{Switch Back to the Main Branch}

\begin{lstlisting}[language=bash]
git checkout main
\end{lstlisting}

\subsection{Merge the Feature Branch}

\begin{lstlisting}[language=bash]
git merge feature-x
\end{lstlisting}

This command merges the changes from `feature-x` into the `main` branch, incorporating your new features or changes into the main project.

\end{document}
